Statistical Theory\\ Chess Dataset Analysis

### 2024-09-29 Article/Article.tex
fixed nothing

    \item \textbf{Resignations}: Games concluded by resignation were removed. A resignation introduces a psychological factor into game length and outcome, which can skew the statistical distribution. By removing these games, we aim to focus on games decided by normal play.

@@

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{allgames.png}
    \caption{Gamma-Poisson distribution fitted to the 'Turns' data}
    \label{fig:all_games}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{ratedgames.png}
    \caption{Gamma-Poisson distribution fitted to the 'Turns' data}
    \label{fig:rated_games}
\end{figure}

\subsection{Rating Distribution}
The distribution of player ratings in the dataset initially resembles a normal distribution with a peak around the mean. However, this peak diminishes when games involving unrated players are excluded, bringing the distribution closer to normality. This is illustrated in Figure~\ref{fig:all_games} and Figure~\ref{fig:rated_games}. Additionally, the QQ plot (Figure~\ref{fig:rating_qq}) supports the similarity between the player rating distribution and a normal distribution, albeit with deviations at the extremes.

>>>>

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{transformation_plot.png}
    \caption{Transformation's effected on Rating and Turns}
    \label{fig:transformation_plot}
\end{figure}

@@

\subsection{Rating Distribution}
The distribution of player ratings in the dataset initially resembles a normal distribution with a peak around the mean. However, this peak diminishes when games involving unrated players are excluded, bringing the distribution closer to normality. This is illustrated in Figure~\ref{fig:transformation_plot}. Additionally, the QQ plot (Figure~\ref{fig:rating_qq}) supports the similarity between the player rating distribution and a normal distribution, albeit with deviations at the extremes.
